Consistent ecosystem functional response across precipitation extremes in a sagebrush steppe

### 2017-08-23 manuscript/usses_water_ms.Rmd
tiny ms update

  **Methods.** We conducted a five year precipitation manipulation experiment in a sagebrush steppe ecosystem in Idaho, US. We used drought and irrigation treatments (approximately 50% decrease/increase) to investigate whether ecosystem functional response remains consistent at extreme precipitation levels. We recorded data on aboveground net primary productivity (ANPP), species abundance, and soil moisture. We fit a random intercept, random slope model to determine if the relationship between ANPP and soil moisture differed among treatments. We used nondimensional multivariate scaling to quantify community composition over the five years.

  **Results.** Ecosystem functional response, defined as the relationship between soil moisture and ANPP, did not vary across drought, control, and irrigation treatments. ANPP responded positively to availabile soil moisture, but the response was weak and uncertain. There was also no evidence that treatment effects grew over time. Plant community composition was remarkably stable over the course of the experiment and did not differ among treatments.

>>>>

  **Methods.** We conducted a five year precipitation manipulation experiment in a sagebrush steppe ecosystem in Idaho, US. We used drought and irrigation treatments (approximately 50% decrease/increase) to investigate whether ecosystem functional response remains consistent at extreme precipitation levels. We recorded data on aboveground net primary productivity (ANPP), species abundance, and soil moisture. We fit a generalized linear mixed effects model to determine if the relationship between ANPP and soil moisture differed among treatments. We used nondimensional multivariate scaling to quantify community composition over the five years.

  **Results.** Ecosystem functional response, defined as the linear relationship between soil moisture and ANPP, was similar among drought and control treatments, but the irrigation treatment had a slightly lower slope. ANPP responded positively to availabile soil moisture, but the response was weak and uncertain regardless of treatment. There was also no evidence that treatment effects grew over time. Plant community composition was remarkably stable over the course of the experiment and did not differ among treatments.
